---
title: "p8105_hw6_lx2346"
author: "linshan"
date: "2024-11-17"
output: github_document
---
Load the packages
```{r}
library(tidyverse)
library(modelr)
```


## Problem 1
Use the code chunk below to download the data.
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
``` 

Generate 5000 bootstrap samples.
```{r}
boot_straps = 
  weather_df |>
  modelr::bootstrap(5000)|>
  mutate(
    strap = map(strap, as_tibble),
    models = map(strap, \(df) lm(tmax ~ tmin, data = df))) 
```

Clean the result and produce estimates of ğ‘ŸÌ‚2 ,ğ›½Ì‚0 and ğ›½
```{r}
weather_result = 
  boot_straps |>
  mutate(result_1 = map(models, broom::tidy)) |>
  unnest(result_1) |>
  select(.id, models, term, estimate) |>
  pivot_wider(
    id_cols = c(.id, models),
    names_from = term,
    values_from = estimate
  ) |>
  select(.id, models,
    beta0 = `(Intercept)`,
    beta1 = tmin) |>
  mutate(
    log_b0_b1 = log(beta0 * beta1)
  ) |>
  mutate(result_2 = map(models, broom::glance)) |>
  unnest(result_2) |>
  select(.id, beta0, beta1, log_b0_b1, r.squared)
```
## Plot the distribution of your estimates, and describe these in words
```{r}
weather_result |>
  ggplot(aes(x = r.squared)) + 
  geom_histogram(binwidth = 0.01, fill = "skyblue", color = "black") +
  theme_minimal() +
  labs(title = "Bootstrap Distribution of R-squared", x = "R-squared")

weather_result |>
  ggplot(aes(x = log_b0_b1)) + 
  geom_histogram(binwidth = 0.01, fill = "pink", color = "black") +
  theme_minimal() +
  labs(title = "Bootstrap Distribution of log(Î²0 * Î²1)", x = "log(Î²0 * Î²1)")
```
\
**Comment**:It can be observed that the R-squared values are concentrated around 0.9, approximately forming a bell shape. The distribution of log(Î²â‚€ * Î²â‚) ranges from 1.90 to 2.10, with a peak around 2.01, also exhibiting a bell-shaped pattern.

## Identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for ğ‘ŸÌ‚2 and log(ğ›½Ì‚0âˆ—ğ›½Ì‚1).
```{r}
ci_r2 = quantile(weather_result$r.squared, c(0.025, 0.975))
ci_log_beta = quantile(weather_result$log_b0_b1, c(0.025, 0.975))
tibble(
  ci_r2 = ci_r2,
  ci_log_beta = ci_log_beta)
```





